Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-05 paper/v1.0/sections/4_inverse_scattering_time.tex
Corrections

In addition, for a scenario of scattering take place inside the same Landau level, we are able to present the delta distribution of the energy using the following interpretation \cite{dini16}
\begin{equation} \label{eq_16}
 \delta(\varepsilon - \varepsilon_{N}) \approx
 \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)}.
\end{equation}
Then we can write the central element of inverse scattering time matrix in more compact form
\begin{equation} \label{eq_17}
  \begin{aligned}
    \Gamma^{00}_{N}(\varepsilon,& k_x) =
    \varrho
    \bigg[
    \int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2
    \bigg]^{-\frac{1}{2}},
  \end{aligned}
\end{equation}
where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
To analyze the effect done by the dressing field on the scattering-induced broadening, we can introduce normalized $N$-th Landau level scattering-induced broadening as
\begin{equation} \label{eq_18}
    \Lambda_N(k_x) \equiv
    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
\end{equation}
and this leads to
\begin{widetext}
\begin{equation} \label{eq_19}
    \Lambda_N (k_x) =
    \qty[
    \frac
    {\int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1])
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    {\int_{-\infty}^{\infty} d {k}_1 \;
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{0}\qty(\lambda_2 k_2)
    \tilde{\chi}_{0}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    ]^{1/2}.
\end{equation}
\end{widetext}

Normalized energy band broadening against x-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and results are depicted in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}). To make a comparison, we have selected the experiment parameters to match with analysis done in Ref.~\cite{endo09}.
In their study, they have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\tilde{m}_e$ where $\tilde{m}_e$ is mass of the electron \cite{endo09,winkler03,wackerl20}. In addition, they used the broadening of the natural(without a dressing field) $0$-th Landau level $\Gamma_0$ as $0.24\;\text{me}V$. Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
Here we can identify that the normalized energy broadening value for each Landau level is independent of the x-directional momentum $k_x$ value and we are able to manipulate it by the dressing field. When the dressing field's intensity increase, the energy broadening gets reduced and this make adjustments in transport properties. In the next section, we are going to derive a analytical expression for the conductivity in dressed quantum Hall systems to analyze these adjustments.

>>>>

In addition, for a scenario of scattering take place inside the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
\begin{equation} \label{eq_16}
 \delta(\varepsilon - \varepsilon_{N}) \approx
 \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)}.
\end{equation}
Then we write the central element of inverse scattering time matrix in more compact form
\begin{equation} \label{eq_17}
  \begin{aligned}
    \Gamma^{00}_{N}(\varepsilon,& k_x) =
    \varrho
    \bigg[
    \int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2
    \bigg]^{-\frac{1}{2}},
  \end{aligned}
\end{equation}
where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
To analyze the effects done by the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
\begin{equation} \label{eq_18}
    \Lambda_N(k_x) \equiv
    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
\end{equation}
and this can evaluate with
\begin{widetext}
\begin{equation} \label{eq_19}
    \Lambda_N (k_x) =
    \qty[
    \frac
    {\int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1])
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    {\int_{-\infty}^{\infty} d {k}_1 \;
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{0}\qty(\lambda_2 k_2)
    \tilde{\chi}_{0}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    ]^{1/2}.
\end{equation}
\end{widetext}

Normalized energy band broadening against x-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and the results are depicted in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}). To make a comparison, we have selected the experiment parameters to match with analysis done in Ref.~\cite{endo09}.
In their study, they have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\tilde{m}_e$ where $\tilde{m}_e$ is mass of the electron \cite{endo09,winkler03,wackerl20}. In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $0.24\;\text{me}V$. Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
Here we observe that the normalized energy broadening value for each Landau level is independent of the x-directional momentum $k_x$ value and we are able to manipulate it by the dressing field. When the dressing field's intensity increase, the energy broadening gets reduced and this adds modifications to the transport properties of the system.
To analyze these adjustments in detail, we derive a analytical expression for the conductivity of a dressed quantum Hall system in the next section.

### 2021-08-05 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Corrections

A general theory for the conductivity in dressed systems with the disorder averaging was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}. Within this theory, the general $x$-directional longitudinal DC limit conductivity has been discribed by
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} &=
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ the Fourier component (see Appendix \ref{appendix_d}) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $s=0$ Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considering two-dimensional system, partial distribution function is given by $f$ and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \Pi- \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \frac{\hbar \omega}{2},
\end{equation}
where $ \varepsilon_N$ are quasienergies of all considering Floquet states. Moreover, $tr[\cdot]$ is the trace of operator.

Then Eq.~(\ref{eq_20}) can be expanded in off resonant regime ($\omega\tau_0 \gg 1$), where $\tau_0$ is the scattering time of the undriven system, using only central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} \equiv \ket{n,k_x}$

@@

where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Then this can evaluate as follows

@@

Since we can diagonalize the impurity averaged Green's functions using unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}. Thus, we evaluate the matrix element of the difference between retarded and advanced Green's functions as

@@

Here we used the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum of all irreducible diagrams \cite{wackerl20,wackerlthesis20}. Applying the matrix elements of the electric current operator in Landau levels (see Appendix \ref{appendix_d}) and
results form Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we can obtain

@@

and after the expansion, the only remaining non-zero term would be

@@

Then using central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression as follows

@@

where $\tilde{{\Gamma}}(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$. We already identified that the inverse scattering time matrix's central element is independent of $k_x$ value and we can get the sum over all available momentum space in $x$ direction.

@@

Then we use the Fermi-Dirac distribution as our partial distribution function ($f$) for our system

@@

where $k_B$ is Boltzmann constant, $T$ is absolute temperature and $\varepsilon_F$ is Fermi energy of the system. Considering the above distribution with extremely low temperature conditions, we can approximate

@@

and by letting $\Pi = \varepsilon_F$, the expression for conductivity leads to

@@

Same as above derivation, we can derive the longitudinal conductivity in $y$-direction by using the current operator derived in Appendix \ref{appendix_d}

>>>>

A general theory for the conductivity of a dressed system with the disorder averaging was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}. Within this theory, the general $x$-directional longitudinal DC-limit conductivity has been discribed by
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} &=
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are the $x$-directional electric current operator matrix elements' $0$-th Fourier component and the white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considering two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \Pi- \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \frac{\hbar \omega}{2}.
\end{equation}
Here, $ \varepsilon_N$ are quasienergies of all considering Floquet states, and $tr[\cdot]$ is the trace of the considering operator.

Next, we restrict our analysis into off-resonant regime $\omega\tau_0 \gg 1$), where $\tau_0$ is the scattering time of the undriven system. Thus, the $x$-directional longitudinal conductivity given in
Eq.~(\ref{eq_20}) can be expanded using only the central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} \equiv \ket{n,k_x}$

@@

where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Next, we evaluate the above expression as follows

@@

We can diagonalize the impurity averaged Green's functions using a unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) as mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}. Thus, we evaluate the matrix element of the difference between retarded and advanced Green's functions as

@@

Here we introduced the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum of all irreducible diagrams \cite{wackerl20,wackerlthesis20}. Applying the matrix elements of the electric current operator in Landau levels and
expressions form Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we obtain

@@

For the full derivation of electric current operators in quantum Hall system refer to Appendix \ref{appendix_d}.
After the expansion, the only non-zero term would be

@@

Aterwards, considering only the central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression in \ref{eq_27} as follows

@@

with $\tilde{{\Gamma}}(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$. Since we already identified that the inverse scattering time matrix's central element is independent of $k_x$ value, we can drop the $k_x$-dependent in the $\tilde{{\Gamma}}(\varepsilon_n,k_x)$ terms and get the sum over all available momentum space in $x$ direction.

@@

We use the Fermi-Dirac distribution as our partial distribution function ($f$) for our system

@@

where $k_B$ is theBoltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system. Considering the above distribution with extremely low temperature conditions, we use thee following approximation

@@

and by letting $\Pi = \varepsilon_F$, the derived expression in \ref{eq_29} leads to

@@

Following the same steps as above derivation, we can derive the longitudinal conductivity in $y$-direction by applying the electric current operator for $y$-direction derived in Appendix \ref{appendix_d}
